Context Aware Virtual Assistant with Case-Based Conflict Resolution in Multi-User Smart Home Environment

### 2018-01-26 Paper/Paper.tex
Update of Paper

\graphicspath{ {Images/} }

@@

    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Jose Quinde Li Say Tan \inst{2} \and Kenzhegali Nurgaliyev \inst{1}}

@@

    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}}

@@

        Primarily, the main purpose of the research is to create user friendly interface with adaptive context aware

@@

    \cite{5,6} that resolves conflicts between automated devices such as fire alarms and automated door locks.
    On the other hand, these solutions resolves conflicts only between automated devices based on priorities of their rules.

@@

    developers are focused on preference Rule-Based Reasoning (RBR) to resolve conflicts between users \cite{9}. Even through
    these systems introduces efficient set of rules, they are not able to handle with adaptation to the new user cases or
    specific out-of-rule situations. \\

@@

    voice and text based dialogue graphical web user interface for multiple users and resolve conflicts in changing environment.\\

@@

    Technical details of the system are given in this section.
    It consider architecture diagram of the system and explanation of all functional units called modules each

@@

    Moreover, arguments priorities was established by personal user preferences \cite{11} because

@@

    between user and system more natural \cite{7}.\\

@@

    environment as the Smart Home \cite{10}.

@@

    As a result, each functional part (module) of the system is designed to execute complete task and some of them are
    divided into components.

@@

    Layer is functional components of the system that sequentially divides it into hierarchical groups that
    communicates only with layer above or layer below except Database layer.
    For example, Cloud API layer is consists of Speech Generation and Speech Recognition that communicate only with
    Front End layer and Core layer.\\

@@

    Hexagonal icon with white image inside colored blue and text below is module of the system.

@@

    All communication inside the system is demonstrated as arrows in the Fig.1.

@@

    \subsection{Graphical User Interface and Front End}

@@

    Graphical User Interface (GUI) is expressed by 3 functional and Login pages.
    In the Login Page user chooses account.
    User communicates with system in form of dialogue by voice or text chat,
    gives orders \footnote{Order is command of the user given to the system.
    For example, turn off the light.} and reasons \footnote{Reason is argument given by the user to the system to
    justify his/her order.
    For example, turn off the light, because my eyes hurts.} in the Control Page.
    Rules Page and Preference Page are database table editing pages where user changes rules \footnote{Rule is set of instructions given for system to do automatically.
    For example, system is obligated keep kettle turned off from 11:00 till 13:00 everyday because of energy saving issue.} and preferences.\\

@@

    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.
    \subsection{Cloud API}
    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API \footnote{More information on https://w3c.github.io/speech-api/speechapi.html.}.

@@

    Core System is main functional layer of the system.
    Consequently, functions as decision-making, dialogue compilation, text classification and device controlling are all executed in the modules inside the Core System layer.
    It consists of Dialogue Manager, Classification Component, Rule-Based Reasoner, Case-Based Reasoner and Device Control Unit.

@@

    As a result, they need classification algorithm.\\

@@

    \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words (stemmed by LancasterStemmer from Natural Language Toolkit library) inside the text that is already cleaned from punctuation and meaningless words like articles.
    In a text document a word may exist in a different morphological variants.
    For example the word “love” may also exist in other morphological variants such as “loving”, “loved”.
    While these morphological variants are different word forms, that represent same concept.

@@

    \em Output layer \em gives vector of possibilities that the text is inside of classes \footnote{Class is the group of reasons for Reason Classification and group of orders for Order Classification.}.

@@

    While training the ANN it was concluded that the accuracy of the neural network does not significantly changes between one hidden layer neural network and multiple hidden layer neural network.
    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was calculated by
    1000 iterations of Backpropogation training algorithm with standard training/test set especially created for this experiment.\\

@@

    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.
    The system normally does not accept any classification lower that 30\% possibility, and if user says something not
    correlated to the predefined preferences, the system will skip classification and ask again.\\

@@

        System classified it as: [['Work', 0.99951473383654765], ['Health', 0.056650409249493161], ['Entertainment', 0.0011293354032656073], ['Energy', 1.4169164768812246e-05], ['Security', 1.238332260956378e-05], ['Food', 3.1674436013529605e-07]]

@@

    It was used Backpropogation method for the synapses optimisation.
    The Backpropagation learning rule based on supervised learning \cite{14}.

@@

    Training and testing sets were created specially for this experiment.
    There were used common English phrases and their synonyms to create set of sentences and their class.
    During training, the connection weights of the neural network are initialized to random values.
    The training examples in the training set are then presented to the neural network classifier in random order, and
    the connection weights are adjusted according to the Backpropagation learning rule.
    This process is repeated until the learning error falls below a predefined tolerance level (99.95\%).\\

@@

    If there is conflict it executes Case-Based Reasoner (CBR).\\

@@

    Dialogue Manager is one of the central modules of the system.
    Dialogue Manager receives phrases from the user and classifies it by Classification component and sends it to Rule-Based Reasoner.
    Based on the data from Rule-Based Reasoner and actions done by the system it sends human readable report or response to user.\\
    Smart Home environment of the Farm Side Middlesex University is driven by Vera Secure system.
    In consequence, we developed API to communicate with it that is represented by Device Control Unit in the architecture diagram.

@@

    It shows three main scenarios\footnote{Scenario - set of similar cases} inside the system.\\

@@

        \includegraphics[width=\textwidth]{UML.png}

@@

    In order to describe system lifelines, there is explanation of the scenarios.

@@

    In the settings pages the user changes database (3.1 - 3.4).

@@

    To evaluate the system we have constructed randomised double-blind experiment.

@@

    Secondly, it provides such instructions to testers that he or she was
    asked to provide command and arguments in their own words.

@@

    Furthermore, they were provided with additional text box under each question to justify their answers if they though
    that they need to be justified and one more question about what they would include or change in the system.\\

@@

    has 2.9 average value with 1.2 standard deviation amount.
    The basic quantitative analysis of the answers are shown in the figure below.\\
        \includegraphics[width=\textwidth]{eval.png}
        \caption[]{Quantitative analysis of the answers}
    The question about conflict resolution quality was the most hard for the system, because it has two negative answers.

@@

    As a result, there is a list of possible cause effects and ways to solve them:\\
    \begin{enumerate}
        \item Lack of training data: create more training cases and store them into Databases.
        \item Ineffective distance measurement algorithm: replace k-Nearest Neighbor algorithm with Artificial Neural Network or other machine learning algorithm. Combination of heuristic algorithms gives higher results than separately \cite{12}.
        \item Ineffective input matrix: replace input variables by new system that will take into account difference between reasons.
    \end{enumerate}

@@

    The validation tests feedback is positive.

@@

    it is significant to introduce behaviour adapting sub-system \cite{2}.\\

@@

    Furthermore, there is well structured and full observing documentation is available on Wiki page of the system \footnote{https://github.com/BiggyBaron/VirtualAssistant/wiki}.

>>>>

\graphicspath{{Images/}}

@@

    \author{Bauyrzhan Ospan\inst{1} \and Nawaz Khan \inst{2} \and Juan Augusto \inst{2} \and Mario Quinde \inst{2} \inst{3} \and Kenzhegali Nurgaliyev \inst{1}}

@@

    \and Department of Computer Science, Middlesex University, The Burroughs, London NW4 4BT, United Kingdom \\ \email{{N.X.Khan,J.Augusto,MQ093}@live.mdx.ac.uk}
    \and Department of Industrial and Systems Engineering, Universidad de Piura, Av. Ramon Mujica 131, Urb. San Eduardo, Piura, Peru\\
    \email{mario.quinde@udep.pe}}

@@

        The main purpose of the research is to create user friendly interface with adaptive context aware

@@

    \cite{5,6} that resolves conflicts between automated devices.
    These solutions resolves conflicts only between automated devices based on priorities.

@@

    developers are focused on preference Rule-Based Reasoning (RBR) \cite{9}.
    Even through
    these systems introduce efficient set of rules, they are not able to handle with adaptation. \\

@@

    voice and text based dialogue graphical web user interface for multiple users and resolve conflicts in changing environment.

@@

    Technical details of the system
    consider architecture diagram of the system and explanation of all functional units called modules

@@

    Moreover, argument priorities were established by personal user preferences \cite{11} because

@@

    between user and system more natural \cite{7}.

@@

    environment as the Smart Home \cite{10}.\\

@@

    As a result, each functional part (module) of the system is designed to execute complete task.

@@

    Layer is functional level of the system that sequentially divides it into hierarchical groups that
    communicates only with layer above or layer below except Database layer.\\

@@

    Blue hexagonal icon with white image inside and text below is module of the system.

@@

    All communications inside the system is demonstrated as arrows in the Fig.1.

@@

    \subsection{Graphical User Interface, Front End and Cloud API}

@@

    Graphical User Interface (GUI) is expressed by 3 functional and one login pages.\\

@@

    Last but not the least, right hand side of the interface is filled by devices status indicators that shows current statuses.\\
    The function units of the Speech Generation and Speech Recognition were established via W3C Web Speech API.

@@

    Core System is main functional layer.
    Consequently, functions as decision-making, dialogue compilation, text classification and device controlling are all executed in the Core System.
    It consists of Dialogue Manager, Classification Component, Rule-Based Reasoner, Case-Based Reasoner and Device Control Unit.\\

@@

    As a result, they need classification algorithm.

@@

    \em Input layer \em consist of input neurons that are binomial representation of the unique stemmed words inside the text that is already cleaned from punctuation and meaningless words like articles.
    While morphological variants are different word forms, they represent same concept.

@@

    \em Output layer \em gives vector of possibilities that the text is inside of classes.

@@

    The most efficient number of hidden layer neurons (14) was found by calculation of the delta that was found by
    1000 iterations of Backpropogation training algorithm.\\

@@

    Classifier says that it is 99.9\% about work, and a little bit (0.05\%) about heath issue, because his project about flu.\\

@@

        System classified it as: 'Work': 0.999, 'Health': 0.0566

@@

    The Backpropagation learning rule based on supervised learning was used \cite{14}.

@@

    Training and testing sets were created specially for this experiment.\\

@@

    If there is a conflict it executes Case-Based Reasoner (CBR).\\

@@

@@

    It shows two main scenarios inside the system.\\

@@

        \includegraphics[width=0.7\textwidth]{UML.png}

@@

@@

@@

@@

    Secondly, it provides such instructions to testers where he or she was
    asked to provide commands in their own words.

@@

    Furthermore, they were provided with additional text box under each question to justify their answers.\\

@@

    has 2.9 average value with 1.2 standard deviation amount.\\
    The question about conflict resolution quality was the most complicated for the system, because it has two negative answers.

@@

    As a result, there is a list of possible cause effects and ways to solve them.
    Firstly, lack of training data can be solved by creating more training cases and store them into Databases.
    Second, changing the input matrix formulation might be solution.\\

@@

    The validation tests feedback is positive.\\

@@

    it is significant to introduce behaviour adapting sub-system \cite{2}.

@@
